---
title: |
  \vspace*{\fill}
  \fontsize{36}{40}\selectfont \textbf {Forecasting Bikeshare Demand Using Time Series Analysis}
author: |
  \fontsize{24}{28}\selectfont Seif H. Kungulio
date: |
  \fontsize{18}{22}\selectfont December 19, 2025
  \ \vspace*{\fill}
output: 
  pdf_document:
    latex_engine: xelatex
    toc: false
    highlight: espresso
    include:
      in_header: resources/header.tex
header-includes:
  # Font and color setup
  - \usepackage{xcolor}
  - \definecolor{brand}{HTML}{ff4000}
  - \definecolor{subbrand}{HTML}{143d0d}
  - \usepackage{titlesec}
  - \titleformat{\section}{\Large\bfseries\color{brand}}{\thesection}{1em}{}
  - \titleformat{\subsection}{\large\bfseries\color{subbrand}}{\thesubsection}{0.75em}{}
  - \usepackage[most]{tcolorbox}
  - \tcbset{colback=white, colframe=brand, coltitle=white, fonttitle=\bfseries}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{brand}{Forecasting Bikeshare Demand}}
  - \fancyhead[R]{\textcolor{subbrand}{Seif H. Kungulio}}
  - \fancyfoot[C]{\thepage}
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)

# Set default CRAN mirror
options(repos = c(CRAN = "https://cloud.r-project.org"))

#Install the following libraries if required
# List of required packages
required_pkgs <- c("tidyverse", "lubridate", "skimr", "janitor", "scales", "glue", 
                   "fabletools", "feasts", "yardstick", "tsibble", "fable", "knitr") 

# Install and load each package
for (pkg in required_pkgs) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
  }
  library(pkg, character.only = TRUE)
}

theme_set(theme_test(base_size = 14))
options(dplyr.summarise.inform = FALSE)
```

\pagenumbering{gobble}

\newpage
\thispagestyle{plain}
&nbsp;

\newpage
\pagenumbering{roman}
\tableofcontents

\newpage
\pagenumbering{arabic}

# **Business Understanding**
## Introduction


## Problem Statement


## Objectives


## Key Stakeholders


## Project Scope


## Success Criteria



\newpage

# **Data Understanding**
## Dataset Overview


## Data Loading
```{r}
day_raw <- read_csv("resources/data/day.csv")
glimpse(day_raw)
```

```{r}
hour_raw <- read_csv("resources/data/hour.csv")
glimpse(hour_raw)
```

```{r}
skimr::skim(day_raw)
```

## Data Exploration


## Initial Findings


## Summary of Insights




\newpage

# **Data Preparation**
## Data Cleaning
```{r}
day_raw %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "missing_count") %>%
  arrange(desc(missing_count)) %>%
  kable(caption = "Missing Values i n Day Dataset")
```

## Feature Engineering
```{r}
day <- day_raw %>%
  mutate(date = as_date(dteday),
         year = year(date),
         month = month(date, label = TRUE),
         weekday = wday(date, label = TRUE),
         weekend = if_else(weekday %in% c("Sat", "Sun"), 1, 0)) %>%
  select(date, year, month, weekday, weekend, temp, atemp, hum, windspeed, casual, registered, cnt)
glimpse(day)
```

```{r}
day <- day_raw %>%
  mutate(
    dteday = as.Date(dteday),
    year = ifelse(yr == 0, 2011, 2012),
    month = month(dteday, label = TRUE),
    weekday = wday(dteday, label = TRUE),
    weekend = if_else(weekday %in% c("Sat", "Sun"), 1L, 0L)
  ) %>%
  arrange(dteday) %>%
as_tsibble(index = dteday)

day %>%
  has_gaps()
```

```{r}
summary(day$cnt)
stopifnot(nrow(day) == 731)  # expected daily records per dataset description
```

## Data Transformation


## Final Dataset Summary


## Data Quality Report


## Data Dictionary


## Summary of Preparation Steps





\newpage

# **Modeling**
## Modeling Approach


## Model Development


## Model Evaluation


## Model Selection


## Summary of Modeling Steps




\newpage

# **Evaluation**
## Results Summary


## Business Impact Assessment


## Lessons Learned


## Recommendations




\newpage

# **Deployment**
## Deployment Plan


## Monitoring and Maintenance Strategy


## Future Work Suggestions


## Summary of Deployment Steps


## Acknowledgments


## About the Author


## Appendix: Code Listings


## Additional Visualizations


## Glossary of Terms


## Data Sources


## Contact Information


## Feedback and Questions




\newpage

# **Conclusion**
## Project Summary


## Key Takeaways


## Final Thoughts






\newpage
&nbsp;

\newpage
# **References**
## List of References


## Citation Style Used


## Additional Reading Materials


## Acknowledgment of Sources






\newpage

# **Appendix**
